\section{Conclusions}
\label{conc}

%Conclusion text...
%
%Length: 0.25-0.5 pages max (1-2 pgfs)
%
%Summary of key contributions (should match your design goals).
%Not summary of whole paper.  Any novel contributions mentioned.
%Summarize good eval results.
%
%Key: give reader the "take home" message.

We found important nodes in an ego network using different centrality
measures.  Also we found the important nodes by dividing the ego
network using k-means clustering and reporting the centroid as the
important node.  We see that eigenvector centrality is the most
accurate measure of identifying important nodes.  Closeness centrality
also performs well as compared to betweenness centrality.  We also see
that k-means clustering also identifies the important node when number
of communities are more than 5.  We can conclude that some nodes are
more important than other for one measure, but less important for
different measure.  There are some nodes, that are important for all
kind of measures of importance.

\paragraph{Future Work}
We plan to extend k-means clustering algorithm by not reporting the
centroid of the cluster as important node.  We'll run eigenvector
centrality algorithm on each cluster and then report the important
nodes.  We'll also try to improve the betweenness centrality as
current betweenness centrality algorithm is not applicable to
disconnected graphs.  And presence of ego affects the outcome of the
algorithm severely most of the shortest paths will pass through ego,
and the distance can not be more than 2.

%Future work text...
%
%Typical length: 0.25-0.33 pages max
%
%Don't write too much:
%- the more you write, the more work appears "premature"
%- takes up important space (small impact on acceptance)
%
%Often folded as subsection of conclusions.
%
%Describe most important 1-3 "novel/research" future work ideas.
%
%Avoid "short term" future goals.  Focus on long-term goals, well
%beyond the scope of THIS paper.  Avoid stuff that might be
%considered as should have been part of this work.
%
%Give reader some ideas of HOW you plan to go about investigating
%future ideas.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Emacs:
% Local variables:
% fill-column: 70
% End:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Vim:
% vim:textwidth=70
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LocalWords:
